Revisiting the impact of deepfake technology towards viewer's political choice: A replication of Soubhik Barari (2021)

### 2021-03-18 outputs/paper/paper.Rmd
Update Discussion section

>>>>

This paper replicates the first experiment of Soubhik Barari (2021) to further study the persuasion power of deepfake through the channel of its affective manipulation on viewer’s political perception. Media heterogeneity effects are reviewed via t-tests between other false media and deepfake.  The heterogeneity in affective response by viewer traits is examined with a multiple linear regression model. Feature selection is performed via the Random Forest classifier to select the top 20 relevant variables into our model input, which identified additional important socioeconomic features other than the ones from the original paper.
